Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-19 doc/GMP2015/s01_introduction.tex
Fixed some references and citations. Unified display of OptDRP, ComDRP, CanDRP, use \drp{G}, \optdrp{G}, etc.

    \item More recent, engineered examples, including disordered
    graphene layers~\cite{Graphene1}~\cite{Graphene2} sometimes
    reinforced by microfibrils; and DNA assemblies including a recent
    Sierpinski gasket~\cite{self_assembly_sierpinski}, bringing other
    self-similar structures~\cite{Microfibrils2} within reach.

>>>>

    \item More recent, engineered examples, including disordered
    graphene layers~\cite{Graphene1}~\cite{Graphene2} sometimes
    reinforced by microfibrils; and DNA assemblies including a recent
    Sierpinski gasket~\cite{self_assembly_sierpinski}, bringing other
    self-similar structures~\cite{wikimediacommons2012subdivision} within reach.

### 2014-12-19 doc/GMP2015/s02_preliminaries.tex
Fixed some references and citations. Unified display of OptDRP, ComDRP, CanDRP, use \drp{G}, \optdrp{G}, etc.

    $G$, \cite{hoffman2001decompositionI} {\sl DRP}$(G)$ (see Figure \ref{fig:c2c3ofk33s}, is defined as a forest that has the

@@

    even optimal DR-plans in the size of the graph . A complete DR-
    plan is unique but may not be (is usually not) optimal. DR-plans

@@

\header{Realizing given qusecs.}
Note that this basic task
would require finding real solutions a large multivariate polynomial
system (of inequalities and equalities representing the constraints).
Without DR-planning, this requires double exponential time in the
number of variables (even if orientation type is specified). With DR-
planning, the complexity is dominated by the size of the largest
subsystem that is solved, or recombined from the solutions of its
child subsystems i.e.,the maximum fan-in occuring in a DR-plan. Thus
finding an optimal DR-plan is important for realization.

>>>>

    $G$, \cite{hoffman2001decompositionI} $\drp{G}$ (see Figure \ref{fig:c2c3ofk33s}), is defined as a forest that has the

@@

    even optimal DR-plans in the size of the graph . A complete DR-plan
    is unique but may not be (is usually not) optimal. DR-plans

@@

\header{Realizing given qusecs.}
Note that this basic task
would require finding real solutions a large multivariate polynomial
system (of inequalities and equalities representing the constraints).
Without DR-planning, this requires double exponential time in the
number of variables (even if orientation type is specified). With
DR-planning, the complexity is dominated by the size of the largest
subsystem that is solved, or recombined from the solutions of its
child subsystems i.e.,the maximum fan-in occuring in a DR-plan. Thus
finding an optimal DR-plan is important for realization.

### 2014-12-19 doc/GMP2015/s03_drp.tex
Fixed some references and citations. Unified display of OptDRP, ComDRP, CanDRP, use \drp{G}, \optdrp{G}, etc.

\begin{theorem}\label{theorem:main}
Given an isostatic 2D bar-joint graph $G$ and ComDRP$(G)$, for all nodes $C$ with children $C_1,\ldots,C_N$ keep children according to the following rules.
\begin{enumerate}
    \item If $C_i \cap C_j$ is trivial then keep all $C_1,\ldots,C_N$ as children.
    \item If $C_i \cap C_j$ is isostatic then select any two out of $C_1,\ldots,C_N$ as children.
\end{enumerate}
This covers all cases and the resulting plan is an optimal DR-plan.
\end{theorem}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly well-constrained. As explained in the proof of Theorem \ref{theorem:main}, part 2, since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

>>>>

\begin{theorem}\label{theorem:main}
Given an isostatic 2D bar-joint graph $G$ and $\comdrp{G}$, for all nodes $C$ with children $C_1,\ldots,C_N$ keep children according to the following rules.
\begin{enumerate}
    \item If $C_i \cap C_j$ is trivial then keep all $C_1,\ldots,C_N$ as children.
    \item If $C_i \cap C_j$ is isostatic then select any two out of $C_1,\ldots,C_N$ as children.
\end{enumerate}
This covers all cases and the resulting plan is an optimal DR-plan.
\end{theorem}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the canonical decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly well-constrained. As explained in the proof of Theorem \ref{theorem:main}, part 2, since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

### 2014-12-19 doc/GMP2015/s05_problems.tex
Fixed some references and citations. Unified display of OptDRP, ComDRP, CanDRP, use \drp{G}, \optdrp{G}, etc.

We discuss the complexity of the restricted 
OMD problem (when $k$ is part of the input) 
in Section \ref{sec:conclusion}.

%In the recombination setting, the corresponding \dfn{restricted
%OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
%completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
%or to be a low Cayley complexity tree-decomposable graph as in Section
%\ref{sec:tdecomp}. Clearly these problems have deterministic
%polynomial time algorithms, the algorithms run in time exponential in
%$k$. As a result, when $k$ is part of the input, the \dfn{restricted
%OMD problem} has the potential to be difficult. For example, when the
%isostatic completion $H$ is required to be a 2-tree the restricted OMD
%problem is reducible to the maximum spanning series-parallel subgraph
%problem shown by \cite{cai1993spanning} to be NP-complete even if the input
%graph is planar of maximum degree at most 6. However, since the OMD
%problem has other input restrictions such as not having any proper
%isostatic subgraphs, it is not clear if the reverse reduction exists
%and hence it is unclear whether the OMD problem is NP-complete. The
%same holds for the restricted OMD problem where the isostatic
%completion $H$ is required to be a tree-decomposable graph of low
%Cayley complexity (i.e, have special, small DR-plans). One potential
%obstacle to an indecomposable graph $G$'s membership in the restricted
%OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
%In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
%have been constructed in \cite{servatius2000rigidity}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{sitharam2005combinatorial,joan-arinyo2003transforming,zhang-gao2006well} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{joan-arinyo2003transforming}
requiring the completion to be tree-decomposable. 
%It is not clear if
%the reverse reduction holds, i.e, is OMD reducible to OC?

>>>>

We discuss the complexity of the restricted
OMD problem (when $k$ is part of the input)
in Section \ref{sec:futurework}.

%In the recombination setting, the corresponding \dfn{restricted
%OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
%completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
%or to be a low Cayley complexity tree-decomposable graph as in Section
%\ref{sec:tdecomp}. Clearly these problems have deterministic
%polynomial time algorithms, the algorithms run in time exponential in
%$k$. As a result, when $k$ is part of the input, the \dfn{restricted
%OMD problem} has the potential to be difficult. For example, when the
%isostatic completion $H$ is required to be a 2-tree the restricted OMD
%problem is reducible to the maximum spanning series-parallel subgraph
%problem shown by \cite{cai1993spanning} to be NP-complete even if the input
%graph is planar of maximum degree at most 6. However, since the OMD
%problem has other input restrictions such as not having any proper
%isostatic subgraphs, it is not clear if the reverse reduction exists
%and hence it is unclear whether the OMD problem is NP-complete. The
%same holds for the restricted OMD problem where the isostatic
%completion $H$ is required to be a tree-decomposable graph of low
%Cayley complexity (i.e, have special, small DR-plans). One potential
%obstacle to an indecomposable graph $G$'s membership in the restricted
%OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
%In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
%have been constructed in \cite{servatius2000rigidity}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}\label{obs:OC_to_OMD}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{sitharam2005combinatorial,joan-arinyo2003transforming,zhang-gao2006well} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{joan-arinyo2003transforming}
requiring the completion to be tree-decomposable.
%It is not clear if
%the reverse reduction holds, i.e, is OMD reducible to OC?
